Near instantaneous response of mesophyll conductance to light availability allows shade leaves to lie in wait

### 2015-07-30 manuscript/manuscript_wtc3.Rmd
added ecophys cite

## Whole tree chamber experimental design
Twelve *Eucalyptus tereticornis* seedlings, chosen from a single local Cumberland plain cohort, were planted in March 2013 into 12 whole-tree chambers (WTC) at the Hawkesbury Forest Experiment site near Richmond, NSW, Australia. Each chamber has a maximum height of 10 m and seedlings were grown for 15 months.  A detailed description of the WTC operation and design is available in [@barton2010whole]. Six chambers were set to match outside ambient air temperatures (AT) while the remaining 6 experienced a constant elevated air temperature treatment of +3&deg;C (ET, Figure `r airvars`). The CO~2~ concentration inside the chamber was set to match outside air, tracking diurnal changes. Due to the temperature treatment air humidity was not explicitly controlled. Trees were watered weekly with 70 L from March 2013 to November 2013.  From December 2013 to final harvest trees were watered fortnightly with the mean monthly (100 yr) rainfall amount.  In February 2013 half of the chambers (3 each of AT and ET) were subjected to a drought treatment by withholding watering. Due to a limited range of data for the drought treatment only well-watered trees are reported here.

@@

\
Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C for one sun and shade leaf for each chamber prior to the initiation of the drought treatment. Each AC~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l l^-1^ at 25 &deg;C at saturating light (1800 $\mu$mols m^-1^ s^-1^). From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@Duursma2014] in R [@RDevelopmentCoreTeam2011].

>>>>

## Whole tree chamber experimental design
Twelve *Eucalyptus tereticornis* seedlings, chosen from a single local Cumberland plain cohort, were planted in March 2013 into 12 whole-tree chambers (WTC) at the Hawkesbury Forest Experiment site near Richmond, NSW, Australia. Each chamber has a maximum height of 10 m and seedlings were grown for 15 months.  A detailed description of the WTC operation and design is available in [@barton2010whole]. Six chambers were set to match outside ambient air temperatures (AT) while the remaining 6 experienced a constant elevated air temperature treatment of +3&deg;C (ET, Figure `r airvarsfig`). The CO~2~ concentration inside the chamber was set to match outside air, tracking diurnal changes. Due to the temperature treatment air humidity was not explicitly controlled. Trees were watered weekly with 70 L from March 2013 to November 2013.  From December 2013 to final harvest trees were watered fortnightly with the mean monthly (100 yr) rainfall amount.  In February 2013 half of the chambers (3 each of AT and ET) were subjected to a drought treatment by withholding watering. Due to a limited range of data for the drought treatment only well-watered trees are reported here.

@@

\
Photosynthetic CO~2~ response (AC~i~) curves were measured at 25 &deg;C for one sun and shade leaf for each chamber prior to the initiation of the drought treatment. Each AC~i~ curve began at the reference [CO~2~] of 400 $\mu$l l^-1^ and then consisted of 12 additional steps from [CO~2~] of 50 to 1800 $\mu$l l^-1^ at 25 &deg;C at saturating light (1800 $\mu$mols m^-1^ s^-1^). From these curves the photosynthetic parameters, J~max~ and Vc~max~, were quantified using the biochemical model of [@farquhar1980biochemical] and fit with the 'plantecophys' package [@duursma2015] in R [@RDevelopmentCoreTeam2011].
